\newpage
\section{New Objects Transportation Test}

\subsection{Purpose and Focus of the Test}
The collection of freely available objects lying on a manipulation zone is the core capability of \RCAW-robots. The \iaterm{New Objects Transportation Test }{NOT} includes a new and realistic objects set to grasp. The challenge extends the standard Basic Transportation Test~\ref{sec:Basic Transportation Test} where the robot has transport only basic objects.

\subsection{Scenario Environment}
Basically the BTT2 scenario will be used but with the objects defined in section~\ref{sec:new_objects}. This includes all basic manipulation objects from Table \ref{manipulation_objects} and future objects from Table~\ref{tab:new_objects1} and Table~\ref{tab:new_objects2}.

\subsection{Task}
The task is the same as for a BTT2, with the modification that rocking objects will be replaced by the objects from section~\ref{sec:new_objects}. 


\subsection{Rules}
The following rules have to be obeyed:

\begin{itemize}
	\item A single robot is used.
	\item Six objects have to be picked.
	\item There must be at least 3 decoy objects which must not be picked.
	\item The robot has to start from outside the arena and to stop in the goal area.
	\item A manipulation object counts as successfully grasped as specified in Section~\ref{ssec:GraspingObjects}.
	\item The run is over when the robot reached the final place and the human worker successfully assembled the components or the designated time has expired.
	\item The order in which the teams have to perform will be determined by a draw.
	\item At the beginning of a team's period, the team will get the task specification.
\end{itemize}

\subsection{Scoring}
\begin{itemize}
	\item 200 points are awarded for each correctly and successfully picked object
	\item 125 points are awarded for each correctly placed object.
	\item Standard scoring applies for all other aspects
\end{itemize}
