% !TEX root = ../Rulebook.tex

In the medium term, the \RCAW aims to transfer specific aspects of industrial scenarios in the tests and to demonstrate the practical applicability of the solutions. The challenges, which are adapted or redefined annually, serve as a test platform for the further development of the competitions. Each technical challenge is separately awarded. That means, teams can participate in any number of them. Hoewever any challenge will only be awarded if at least two teams competed unless the only competing team provided an outstanding performance.

A challenge increases the level capabilities of a robot in \RCAW related to:

\begin{itemize}
  \item \textbf{Variability of the environmental conditions} ... The setup conditions of a run are designed variably including disturbances. The lighting situations in the arena are changed dynamically, the configuration of the tables (height, format) is adapted or manipulation objects are mixed with unknown decoy objects.
  \item \textbf{Complexity of the scenarios} ... New arena elements are involved in a scenario
  or its dimensions (size, duration) are increased. This includes, for example, multi-robot scenarios, assembly tasks or new interaction stations.
\end{itemize}

For a successful implementation either an existing solution has to be increased in robustness or a new approach for an additional task has to be developed. The challenges here lie in the fields of perception, manipulation, navigation and planning.

This years challenges try to introduce the relatively new atwork-commander and the planned set of new objects (see \ref{sec:new_objects}).
These changes seem highly important for the participation of new teams, which is why we encourage every team to participate in atleast one technical challenge.

The exact test definition is still missing at the moment, but as the challenges are not part of the main scoring system, some of the rules may be adjusted to the requirements of the teams.

\begin{comment}
\begin{figure}[h!]
  \centering
  \begin{tikzpicture}
  	\begin{polaraxis}[
        xtick ={0, 90, 180, 270},
        xticklabels= {Manipulation, Perception, Navigation, Planning},
        width=5.5cm,
        height=5.5cm,
        legend pos=outer north east,
    ]
  	\addplot
  		coordinates {(0,1.5) (90,3) (180, 0.5) (270,0.5) (0, 1.5)};  % cp
      \addlegendentry{Cluttered Pick Test}
    \addplot
    	coordinates {(0,3) (90,1.5) (180,1) (270,1) (0,3)};  % pfd
      \addlegendentry{Pick from Drawer Test}
  	\end{polaraxis}
  \end{tikzpicture}
  \label{Examplary Challenge introducing a long term operation based on an extended Final test}
\end{figure}

The challenges of 2021 focussing on perception and manipuation in two scenarios. While "Cluttered Pick Test" (CP) adresses the robustness of perception, the "Pick from Drawer Test" (PFD) is focused on additional complexity by including objects in a drawer. Additonally, the start of a league specific simulator, to ease entry of new teams and enable better scientific evaluation is to be established through Simulation Evaluation Test (SE).

\end{comment}

\input{./technical_challenges/MasterCtrlCom}
%\input{./technical_challenges/RealObjectChallenge}
\input{./technical_challenges/CoworkerAssemblyChallenge}
%\input{./technical_challenges/RMC.tex}