\newglossaryentry{Manipulator}
{
	name=Manipulator,
	description={Manipulator is defined as the combination of arm and gripper.}
}
\newglossaryentry{Arm}
{
	name=Arm,
	description={Arm is defined as only the robot arm without the gripper.}
}
\newglossaryentry{Gripper}
{
	name=Gripper,
	description={Gripper is defined as only the gripper without the arm.}
}
\newglossaryentry{OC}
{
	name=OC,
	description={Organization Committee}
}
\newglossaryentry{TC}
{
	name=TC,
	description={Technical Committee}
}
\newglossaryentry{EC}
{
	name=EC,
	description={Executive Committee}
}
\newglossaryentry{TDP}
{
	name=TDP,
	description={Team Description Paper}
}
\newglossaryentry{START}
{
	name=START,
	description={START is defined as the area where the platform starts his run.}
}
\newglossaryentry{FINISH}
{
	name=FINISH,
	description={FINISH is defined as the area where the platform ends his run.}
}
\newglossaryentry{Wall}
{
	name=Wall,
	description={Wall is defined as physical wall in the arena and is static for the whole competition.}
}
\newglossaryentry{Obstacle}
{
	name=Obstacle,
	description={Obstacle is defined as a semi-static physical obstacle in the arena.}
}
\newglossaryentry{VirtualWall}
{
	name=Virtual Wall,
	description={Virtual Wall is defined as a static red/white Tape in the arena and is static for the whole competition.}
}
\newglossaryentry{VirtualObstacle}
{
	name=Virtual Obstacle,
	description={Virtual Obstacle is defined as a semi-static yellow/black Tape in the arena.}
}
\newglossaryentry{ServiceArea}
{
	name=Service Area,
	description={Service Area is defined as an area where the robot has to perform tasks. This can be at a Table, Rotating Table, Shelf or Precision Placement Table.}
}
\newglossaryentry{Container}
{
	name=Container,
	description={Container is defined as a red or blue industrial plastic stacking boxe with the size 2B }
}
\newglossaryentry{ManipulationZone}
{
	name=Manipulation Zone,
	description={Manipulation Zone is defined as the area at a Service Area in which the Objects has to be grasped or placed by the robot.}
}
\newglossaryentry{ArbitrarySurface}
{
	name=Arbitrary Surface,
	description={Arbitrary Surface is defined as an surface that has not the standard white color. Examples are wood pattern, grass, alufoil etc.}
}
\newglossaryentry{Decoy}
{
	name=Decoy,
	description={Decoy is defined as an Object that don't belong to the standard Objects.}
}
\newglossaryentry{Object}
{
	name=Object,
	description={Object is defined as a standard object that has to be grasped or placed by the robot.}
}
\newglossaryentry{Parcferme}
{
	name=Parc ferme,
	description={Parc ferme is defined as...}
}
\newglossaryentry{RefereeBox}
{
	name=Referee Box,
	description={Referee Box is defined as...}
}




